Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-20 article/article.tex
(+) partition cost and transition cost

In order to evaluate a given partition $P$ at time $t$, a cost $C(P, t)$ needs
to be defined. This cost depend on the workload in each the sector. We give the
following definitions~\cite{Ferrari2017} to represent a high
(respectively normal and low) cost for the partition:
\begin{itemize}
  \item $c_+(P, t) = \sum_{S \in P_t} \delta_{h}(S, t) * p_{high}^{S, t} * |S|^2$
  \item $c_=(P, t) = \sum_{S \in P_t} \delta_{n}(S, t) * p_{norm}^{S} * |S|^{-2}$
  \item $c_-(P, t) = \sum_{S \in P_t} \delta_{l}(S, t) * p_{low}^{S, t} * |S|^{-2}$
\end{itemize}
with $\delta_{h}(P, t)$ (resp. $\delta_{n}(P_t)$ and $\delta_{l}(P_t)$) equal 1
if the probability $p_{high}$ (resp. $p_{normal}$ and $p_{low}$) is superior to
the two others, and 0 otherwise.

It is now possible to assign a cost to each partition. This cost is linear
regarding

>>>>

\subsubsection{Partition cost}

In order to evaluate a given partition $P$ at time $t$, a cost $C(P, t)$ needs
to be defined. This cost depend on the workload in each the sector. We give the
following definitions~\cite{Ferrari2017} to represent a high
(respectively normal and low) cost for the partition:
\begin{itemize}
  \item $c_+(P, t) = \sum_{S \in P_t} \delta_{h}(S, t) * p_{high}^{S, t} * |S|^2$
  \item $c_=(P, t) = 1 / (\sum_{S \in P_t} \delta_{n}(S, t) * p_{norm}^{S} * |S|^{-2}$)
  \item $c_-(P, t) = \sum_{S \in P_t} \delta_{l}(S, t) * p_{low}^{S, t} * |S|^{-2}$
\end{itemize}
with $\delta_{h}(P, t)$ (resp. $\delta_{n}(P_t)$ and $\delta_{l}(P_t)$) equal 1
if the probability $p_{high}$ (resp. $p_{normal}$ and $p_{low}$) is superior to
the two others, and 0 otherwise.

It is now possible to assign a cost to each partition. This cost is linear
regarding $c_+$, $c_=$, $c_-$ and $n$ (cardinal of the partition $P$). The
partition cost is defined as follow:
$$
C(P, t) = \alpha c_+ + \beta c_= + \gamma c_- +\lambda n
$$

The parameters $\alpha$, $\beta$, $\gamma$ and $\lambda$ (all positive)
determine a priority on which parameter to optimize. For instance, a high
value $\alpha$ help to
minimize $c_+$, hence the overall number of sectors with too much tafic.
In a real application, it maybe interesting to order those parmaeters as
follow : $\alpha > \lambda > \beta > \gamma$.

\subsubsection{Transition cost}

In an operational context, each reconfiguration raise the workload for
controllers. This trend needs to be considered and a transition cost needs to
be defined for this matter. A transition is (TODO), and the transition cost is
then:
$$
C_{tr}(P_1, P_2) =
\left\{
\begin{array}{l}
    0 \qquad if \qquad P_1 = P_2 \\
    1 \qquad otherwise
\end{array}
\right.
$$
